E\+R\+I\+K\+A3 is an open-\/source A\+U\+T\+O\+S\+AR OS implementation, \href{http://www.erika-enterprise.com}{\texttt{ available for download}} under \href{http://www.erika-enterprise.com/index.php/erika3/licensing.html}{\texttt{ various licensing terms, including a G\+P\+Lv2 license}}.

This document contains the reference manual for E\+R\+I\+K\+A3, which is divided in the following Chapters\+:

The document is divided in the following Chapters\+:

\tabulinesep=1mm
\begin{longtabu}spread 0pt [c]{*{2}{|X[-1]}|}
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Chapter }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Description  }\\\cline{1-2}
\endfirsthead
\hline
\endfoot
\hline
\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Chapter }&\PBS\centering \cellcolor{\tableheadbgcolor}\textbf{ Description  }\\\cline{1-2}
\endhead
\mbox{\hyperlink{intro}{Introduction to E\+R\+I\+K\+A3 and R\+T-\/\+Druid}} &A first introduction to E\+R\+I\+K\+A3.  \\\cline{1-2}
\mbox{\hyperlink{implemented-standards}{Implemented Standards}} &The OS A\+PI standards implemented in E\+R\+I\+K\+A3.  \\\cline{1-2}
\mbox{\hyperlink{scheduler}{E\+R\+I\+K\+A3 and real-\/time scheduling}} &The scheduling algorithms implemented in E\+R\+I\+K\+A3.  \\\cline{1-2}
\mbox{\hyperlink{system-init}{System and application initialization}} &System initialization details.  \\\cline{1-2}
\mbox{\hyperlink{task-types}{Basic and Extended tasks}} &The task types in E\+R\+I\+K\+A3.  \\\cline{1-2}
\mbox{\hyperlink{stack-sharing}{Stack sharing in E\+R\+I\+K\+A3}} &Stack Sharing in E\+R\+I\+K\+A3.  \\\cline{1-2}
\mbox{\hyperlink{irq}{Interruput handlers}} &I\+RQ handling in E\+R\+I\+K\+A3.  \\\cline{1-2}
\mbox{\hyperlink{resources}{Mutual Exclusion and Shared resources}} &Shared resource handling in E\+R\+I\+K\+A3  \\\cline{1-2}
\mbox{\hyperlink{multicore}{Multicore support}} &Multicore support in E\+R\+I\+K\+A3  \\\cline{1-2}
\mbox{\hyperlink{apireference}{E\+R\+I\+K\+A3 A\+PI reference}} &E\+R\+I\+K\+A3 A\+PI reference.  \\\cline{1-2}
\mbox{\hyperlink{orti}{O\+R\+TI support in E\+R\+I\+K\+A3}} &O\+R\+TI support in E\+R\+I\+K\+A3.  \\\cline{1-2}
\end{longtabu}


Additional information is finally available as well in the \href{http://www.erika-enterprise.com/wiki}{\texttt{ E\+R\+I\+K\+A3 wiki}}, and in the \href{http://www.erika-enterprise.com/forum}{\texttt{ E\+R\+I\+K\+A3 Forum}}. 